### 2021-11-01 R0-Density-Reanalysis/R0-Density-Reanalysis.Rmd
Knitted the paper before sending to source files publisher for production

journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
header-includes:
    - \usepackage{setspace}\onehalfspacing
---

@@

<!--
Install data package as appropriate. The data package is file `r0density_0.1.0.tar.gz`
-->

@@

@@

The objective of this paper is to illustrate the importance of reproducibility in research in the context of the flood of COVID-19 papers. For this, I focus on a recent study by Sy et al. [-@Sy2021population] that examined the correlation between the basic reproductive number of COVID-19, $R_0$, and population density.  The basic reproductive number is a summary measure of contact rates, probability of transmission of a pathogen, and duration of infectiousness. In rough terms, it measures how many new infections each infections begets. The paper of Sy et al. [-@Sy2021population] was selected for being, in the literature examined, almost alone in supporting reproducible research. Accordingly, I wish to be clear that my objective in singling their work for discussion is not to malign their efforts, but rather to demonstrate how open and reproducible research efforts can greatly help to accelerate discovery. More concretely, open data and open code mean that an independent researcher can, with only modest efforts, not only verify the findings reported, but also examine the same data from a perspective which may not have been available to the original researchers due to differences in disciplinary perspectives, methodological traditions, and/or training, among other possible factors. The example, which shows consequential changes in the conclusions reached by different analyses, should serve as a call to researchers to redouble their efforts to increase transparency and reproducibility in their research. In this spirit, the present paper also aims to show how data can be packaged in well-documented, shareable units, and code can be embedded into self-contained documents suitable for review and independent verification. The source for this paper is an [R Markdown](http://rmarkdown.rstudio.com) document which, along with the data package, will be available in a public repository^[For peer-review purposes, the data package and code are currently in an anonymous Drive folder: \url{https://drive.google.com/drive/folders/1cT6tcUc1pJ4aT5ajQ0emO0lyS46P8Ige?usp=sharing}].

@@

>>>>

journal: "Geographical Analysis"
date: "`r Sys.Date()`"
bibliography: [bibliography.bib, packages.bib]
linenumbers: true
#numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
header-includes:
    - \usepackage{setspace}\onehalfspacing
---

@@

```{r install-data-package, include=FALSE}
if(!require(r0density)){
    remotes::install_github("paezha/Reproductive-Rate-and-Density-US-Reanalyzed", 
                         subdir = "r0density")
    library(r0density)
}
```

@@

```{r generate-package-bibliography, include=FALSE}
knitr::write_bib(c(.packages(), 
                   "knitr", 
                   "rmarkdown"), 
                 file = "packages.bib")
```

@@

The objective of this paper is to illustrate the importance of reproducibility in research in the context of the flood of COVID-19 papers. For this, I focus on a recent study by Sy et al. [-@Sy2021population] that examined the correlation between the basic reproductive number of COVID-19, $R_0$, and population density.  The basic reproductive number is a summary measure of contact rates, probability of transmission of a pathogen, and duration of infectiousness. In rough terms, it measures how many new infections each infections begets. The paper of Sy et al. [-@Sy2021population] was selected for being, in the literature examined, almost alone in supporting reproducible research. Accordingly, I wish to be clear that my objective in singling their work for discussion is not to malign their efforts, but rather to demonstrate how open and reproducible research efforts can greatly help to accelerate discovery. More concretely, open data and open code mean that an independent researcher can, with only modest efforts, not only verify the findings reported, but also examine the same data from a perspective which may not have been available to the original researchers due to differences in disciplinary perspectives, methodological traditions, and/or training, among other possible factors. The example, which shows consequential changes in the conclusions reached by different analyses, should serve as a call to researchers to redouble their efforts to increase transparency and reproducibility in their research. In this spirit, the present paper also aims to show how data can be packaged in well-documented, shareable units, and code can be embedded into self-contained documents suitable for review and independent verification. The source for this paper is an [R Markdown](http://rmarkdown.rstudio.com) document which, along with the data package, are available in a public repository^[\url{https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed}].

@@

# Acknowledgments {#acknwledgments .unnumbered}

The analysis reported in this paper was conducted in the `R` computing statistical language [@R-base]. The source document is an Rmarkdown document [@rmarkdown2018; @rmarkdown2020] processed using `knitr` [@knitr2015; @knitr2014]. The following packages were used in the analysis, and I wish to acknowledge their creators for their generous efforts: `adespatial` [@R-adespatial], `censReg` [@R-censReg], `dplyr` [@R-dplyr], `forcats` [@R-forcats], `ggplot2` [@ggplot22016], `gmm` [@gmm2010], `kableExtra` [@R-kableExtra], `Matrix` [@R-Matrix], `maxLik` [@maxLik2011], `miscTools` [@R-miscTools], `mvtnorm` [@mvtnorm2009], `nlme` [@R-nlme], `patchwork` [@R-patchwork], `purrr` [@R-purrr], `readr` [@R-readr], `sampleSelection` [@sampleSelection2008], `sandwich` [@sandwich2020; @sandwich2004; @sandwich2006], `scico` [@R-scico], `sf` [@sf2018], `sp` [@sp2005; @sp2013], `spatialprobit` [@R-spatialprobit], `spData` [@R-spData], `spdep` [@spdep2018; @spdep2013], `stringr` [R-stringr], `tibble` [@R-tibble], `tidycensus` [@R-tidycensus], `tidyr` [@R-tidyr], `tidyverse` [@tidyverse2019], `tmvtnorm` [@R-tmvtnorm], `units` [@units2016]. This research was not supported by Canada's Research Councils.

### 2021-11-01 R0-Density-Reanalysis/R0-Density-Reanalysis.tex
Knitted the paper before sending to source files publisher for production

The objective of this paper is to illustrate the importance of
reproducibility in research in the context of the flood of COVID-19
papers. For this, I focus on a recent study by Sy et al. (2021) that
examined the correlation between the basic reproductive number of
COVID-19, \(R_0\), and population density. The basic reproductive number
is a summary measure of contact rates, probability of transmission of a
pathogen, and duration of infectiousness. In rough terms, it measures
how many new infections each infections begets. The paper of Sy et al.
(2021) was selected for being, in the literature examined, almost alone
in supporting reproducible research. Accordingly, I wish to be clear
that my objective in singling their work for discussion is not to malign
their efforts, but rather to demonstrate how open and reproducible
research efforts can greatly help to accelerate discovery. More
concretely, open data and open code mean that an independent researcher
can, with only modest efforts, not only verify the findings reported,
but also examine the same data from a perspective which may not have
been available to the original researchers due to differences in
disciplinary perspectives, methodological traditions, and/or training,
among other possible factors. The example, which shows consequential
changes in the conclusions reached by different analyses, should serve
as a call to researchers to redouble their efforts to increase
transparency and reproducibility in their research. In this spirit, the
present paper also aims to show how data can be packaged in
well-documented, shareable units, and code can be embedded into
self-contained documents suitable for review and independent
verification. The source for this paper is an
\href{http://rmarkdown.rstudio.com}{R Markdown} document which, along
with the data package, will be available in a public
repository\footnote{For peer-review purposes, the data package and code
  are currently in an anonymous Drive folder:
  \url{https://drive.google.com/drive/folders/1cT6tcUc1pJ4aT5ajQ0emO0lyS46P8Ige?usp=sharing}}.

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

The objective of this paper is to illustrate the importance of
reproducibility in research in the context of the flood of COVID-19
papers. For this, I focus on a recent study by Sy et al. (2021) that
examined the correlation between the basic reproductive number of
COVID-19, \(R_0\), and population density. The basic reproductive number
is a summary measure of contact rates, probability of transmission of a
pathogen, and duration of infectiousness. In rough terms, it measures
how many new infections each infections begets. The paper of Sy et al.
(2021) was selected for being, in the literature examined, almost alone
in supporting reproducible research. Accordingly, I wish to be clear
that my objective in singling their work for discussion is not to malign
their efforts, but rather to demonstrate how open and reproducible
research efforts can greatly help to accelerate discovery. More
concretely, open data and open code mean that an independent researcher
can, with only modest efforts, not only verify the findings reported,
but also examine the same data from a perspective which may not have
been available to the original researchers due to differences in
disciplinary perspectives, methodological traditions, and/or training,
among other possible factors. The example, which shows consequential
changes in the conclusions reached by different analyses, should serve
as a call to researchers to redouble their efforts to increase
transparency and reproducibility in their research. In this spirit, the
present paper also aims to show how data can be packaged in
well-documented, shareable units, and code can be embedded into
self-contained documents suitable for review and independent
verification. The source for this paper is an
\href{http://rmarkdown.rstudio.com}{R Markdown} document which, along
with the data package, are available in a public repository\footnote{\url{https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed}}.

@@

\hypertarget{acknwledgments}{%
\section*{Acknowledgments}\label{acknwledgments}}
\addcontentsline{toc}{section}{Acknowledgments}

The analysis reported in this paper was conducted in the \texttt{R}
computing statistical language (R Core Team, 2021). The source document
is an Rmarkdown document (Xie et al., 2020, 2018) processed using
\texttt{knitr} (Xie, 2015, 2014). The following packages were used in
the analysis, and I wish to acknowledge their creators for their
generous efforts: \texttt{adespatial} (Dray et al., 2021),
\texttt{censReg} (Henningsen, 2020), \texttt{dplyr} (Wickham et al.,
2021), \texttt{forcats} (Wickham, 2021a), \texttt{ggplot2} (Wickham,
2016), \texttt{gmm} (Chaussé, 2010), \texttt{kableExtra} (Zhu, 2021),
\texttt{Matrix} (Bates and Maechler, 2021), \texttt{maxLik} (Henningsen
and Toomet, 2011), \texttt{miscTools} (Henningsen and Toomet, 2019),
\texttt{mvtnorm} (Genz and Bretz, 2009), \texttt{nlme} (Pinheiro et al.,
2021), \texttt{patchwork} (Pedersen, 2020), \texttt{purrr} (Henry and
Wickham, 2020), \texttt{readr} (Wickham and Hester, 2021),
\texttt{sampleSelection} (Toomet and Henningsen, 2008),
\texttt{sandwich} (Zeileis et al., 2020; Zeileis, 2006, 2004),
\texttt{scico} (Pedersen and Crameri, 2020), \texttt{sf} (Pebesma,
2018), \texttt{sp} (Bivand et al., 2013a; Pebesma and Bivand, 2005),
\texttt{spatialprobit} (Wilhelm and de Matos, 2015), \texttt{spData}
(Bivand et al., 2021), \texttt{spdep} (Bivand et al., 2013b; Bivand and
Wong, 2018), \texttt{stringr} {[}R-stringr{]}, \texttt{tibble} (Müller
and Wickham, 2021), \texttt{tidycensus} (Walker and Herman, 2021),
\texttt{tidyr} (Wickham, 2021b), \texttt{tidyverse} (Wickham et al.,
2019), \texttt{tmvtnorm} (Manjunath B G
\textless bgmanjunath@gmail.com\textgreater, 2015), \texttt{units}
(Pebesma et al., 2016). This research was not supported by Canada's
Research Councils.

@@

\leavevmode\hypertarget{ref-R-Matrix}{}%
Bates, D., Maechler, M., 2021. Matrix: Sparse and dense matrix classes
and methods.

@@

\leavevmode\hypertarget{ref-R-spData}{}%
Bivand, R., Nowosad, J., Lovelace, R., 2021. spData: Datasets for
spatial analysis.

@@

\leavevmode\hypertarget{ref-sp2013}{}%
Bivand, R.S., Pebesma, E., Gomez-Rubio, V., 2013a. Applied spatial data
analysis with {R}, second edition. Springer, NY.

\leavevmode\hypertarget{ref-spdep2013}{}%
Bivand, R.S., Pebesma, E., Gomez-Rubio, V., 2013b. Applied spatial data
analysis with {R}, second edition. Springer, NY.

\leavevmode\hypertarget{ref-spdep2018}{}%
Bivand, R., Wong, D.W.S., 2018. Comparing implementations of global and
local indicators of spatial association. TEST 27, 716--748.

@@

\leavevmode\hypertarget{ref-gmm2010}{}%
Chaussé, P., 2010. Computing generalized method of moments and
generalized empirical likelihood with {R}. Journal of Statistical
Software 34, 1--35.

@@

\leavevmode\hypertarget{ref-R-adespatial}{}%
Dray, S., Bauman, D., Blanchet, G., Borcard, D., Clappe, S., Guenard,
G., Jombart, T., Larocque, G., Legendre, P., Madi, N., Wagner, H.H.,
2021. Adespatial: Multivariate multiscale spatial analysis.

@@

\leavevmode\hypertarget{ref-mvtnorm2009}{}%
Genz, A., Bretz, F., 2009. Computation of multivariate normal and t
probabilities, Lecture notes in statistics. Springer-Verlag, Heidelberg.

@@

\leavevmode\hypertarget{ref-R-censReg}{}%
Henningsen, A., 2020. censReg: Censored regression (tobit) models.

\leavevmode\hypertarget{ref-maxLik2011}{}%
Henningsen, A., Toomet, O., 2011. maxLik: A package for maximum
likelihood estimation in {R}. Computational Statistics 26, 443--458.
doi:\href{https://doi.org/10.1007/s00180-010-0217-1}{10.1007/s00180-010-0217-1}

\leavevmode\hypertarget{ref-R-miscTools}{}%
Henningsen, A., Toomet, O., 2019. miscTools: Miscellaneous tools and
utilities.

\leavevmode\hypertarget{ref-R-purrr}{}%
Henry, L., Wickham, H., 2020. Purrr: Functional programming tools.

@@

\leavevmode\hypertarget{ref-R-tmvtnorm}{}%
Manjunath B G \textless bgmanjunath@gmail.com\textgreater, S.W. with
contributions from, 2015. Tmvtnorm: Truncated multivariate normal and
student t distribution.

@@

\leavevmode\hypertarget{ref-R-tibble}{}%
Müller, K., Wickham, H., 2021. Tibble: Simple data frames.

@@

\leavevmode\hypertarget{ref-sf2018}{}%
Pebesma, E., 2018. {Simple Features for R: Standardized Support for
Spatial Vector Data}. {The R Journal} 10, 439--446.
doi:\href{https://doi.org/10.32614/RJ-2018-009}{10.32614/RJ-2018-009}

\leavevmode\hypertarget{ref-sp2005}{}%
Pebesma, E.J., Bivand, R.S., 2005. Classes and methods for spatial data
in {R}. R News 5, 9--13.

\leavevmode\hypertarget{ref-units2016}{}%
Pebesma, E., Mailund, T., Hiebert, J., 2016. Measurement units in {R}. R
Journal 8, 486--494.
doi:\href{https://doi.org/10.32614/RJ-2016-061}{10.32614/RJ-2016-061}

\leavevmode\hypertarget{ref-R-patchwork}{}%
Pedersen, T.L., 2020. Patchwork: The composer of plots.

\leavevmode\hypertarget{ref-R-scico}{}%
Pedersen, T.L., Crameri, F., 2020. Scico: Colour palettes based on the
scientific colour-maps.

@@

\leavevmode\hypertarget{ref-R-nlme}{}%
Pinheiro, J., Bates, D., R-core, 2021. Nlme: Linear and nonlinear mixed
effects models.

@@

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team, 2021. R: A language and environment for statistical
computing. R Foundation for Statistical Computing, Vienna, Austria.

@@

\leavevmode\hypertarget{ref-sampleSelection2008}{}%
Toomet, O., Henningsen, A., 2008. Sample selection models in {R}:
Package {sampleSelection}. Journal of Statistical Software 27.

@@

\leavevmode\hypertarget{ref-R-tidycensus}{}%
Walker, K., Herman, M., 2021. Tidycensus: Load US census boundary and
attribute data as tidyverse and sf-ready data frames.

@@

\leavevmode\hypertarget{ref-ggplot22016}{}%
Wickham, H., 2016. ggplot2: Elegant graphics for data analysis.
Springer-Verlag New York.

\leavevmode\hypertarget{ref-R-forcats}{}%
Wickham, H., 2021a. Forcats: Tools for working with categorical
variables (factors).

\leavevmode\hypertarget{ref-R-tidyr}{}%
Wickham, H., 2021b. Tidyr: Tidy messy data.

\leavevmode\hypertarget{ref-tidyverse2019}{}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.D., François,
R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen,
T.L., Miller, E., Bache, S.M., Müller, K., Ooms, J., Robinson, D.,
Seidel, D.P., Spinu, V., Takahashi, K., Vaughan, D., Wilke, C., Woo, K.,
Yutani, H., 2019. Welcome to the {tidyverse}. Journal of Open Source
Software 4, 1686.
doi:\href{https://doi.org/10.21105/joss.01686}{10.21105/joss.01686}

\leavevmode\hypertarget{ref-R-dplyr}{}%
Wickham, H., François, R., Henry, L., Müller, K., 2021. Dplyr: A grammar
of data manipulation.

\leavevmode\hypertarget{ref-R-readr}{}%
Wickham, H., Hester, J., 2021. Readr: Read rectangular text data.

\leavevmode\hypertarget{ref-R-spatialprobit}{}%
Wilhelm, S., de Matos, M.G., 2015. Spatialprobit: Spatial probit models.

@@

\leavevmode\hypertarget{ref-knitr2014}{}%
Xie, Y., 2014. Knitr: A comprehensive tool for reproducible research in
{R}, in: Stodden, V., Leisch, F., Peng, R.D. (Eds.), Implementing
Reproducible Computational Research. Chapman; Hall/CRC.

\leavevmode\hypertarget{ref-knitr2015}{}%
Xie, Y., 2015. Dynamic documents with {R} and knitr, 2nd ed. Chapman;
Hall/CRC, Boca Raton, Florida.

\leavevmode\hypertarget{ref-rmarkdown2018}{}%
Xie, Y., Allaire, J.J., Grolemund, G., 2018. R markdown: The definitive
guide. Chapman; Hall/CRC, Boca Raton, Florida.

\leavevmode\hypertarget{ref-rmarkdown2020}{}%
Xie, Y., Dervieux, C., Riederer, E., 2020. R markdown cookbook. Chapman;
Hall/CRC, Boca Raton, Florida.

\leavevmode\hypertarget{ref-sandwich2004}{}%
Zeileis, A., 2004. Econometric computing with {HC} and {HAC} covariance
matrix estimators. Journal of Statistical Software 11, 1--17.
doi:\href{https://doi.org/10.18637/jss.v011.i10}{10.18637/jss.v011.i10}

\leavevmode\hypertarget{ref-sandwich2006}{}%
Zeileis, A., 2006. Object-oriented computation of sandwich estimators.
Journal of Statistical Software 16, 1--16.
doi:\href{https://doi.org/10.18637/jss.v016.i09}{10.18637/jss.v016.i09}

\leavevmode\hypertarget{ref-sandwich2020}{}%
Zeileis, A., Köll, S., Graham, N., 2020. Various versatile variances: An
object-oriented implementation of clustered covariances in {R}. Journal
of Statistical Software 95, 1--36.
doi:\href{https://doi.org/10.18637/jss.v095.i01}{10.18637/jss.v095.i01}

\leavevmode\hypertarget{ref-R-kableExtra}{}%
Zhu, H., 2021. kableExtra: Construct complex table with kable and pipe
syntax.

### 2021-11-01 README.Rmd
Knitted the paper before sending to source files publisher for production

---
output:
  github_document:
    pandoc_args: --webtex
always_allow_html: true
bibliography: R0-Density-Reanalysis/bibliography.bib
---

@@

@@

The objective of this paper is to illustrate the importance of reproducibility in research in the context of the flood of COVID-19 papers. For this, I focus on a recent study by Sy et al. [-@Sy2021population] that examined the correlation between the basic reproductive number of COVID-19, $R_0$, and population density.  The basic reproductive number is a summary measure of contact rates, probability of transmission of a pathogen, and duration of infectiousness. In rough terms, it measures how many new infections each infections begets. The paper of Sy et al. [-@Sy2021population] was selected for being, in the literature examined, almost alone in supporting reproducible research. Accordingly, I wish to be clear that my objective in singling their work for discussion is not to malign their efforts, but rather to demonstrate how open and reproducible research efforts can greatly help to accelerate discovery. More concretely, open data and open code mean that an independent researcher can, with only modest efforts, not only verify the findings reported, but also examine the same data from a perspective which may not have been available to the original researchers due to differences in disciplinary perspectives, methodological traditions, and/or training, among other possible factors. The example, which shows consequential changes in the conclusions reached by different analyses, should serve as a call to researchers to redouble their efforts to increase transparency and reproducibility in their research. In this spirit, the present paper also aims to show how data can be packaged in well-documented, shareable units, and code can be embedded into self-contained documents suitable for review and independent verification. The source for this paper is an [R Markdown](http://rmarkdown.rstudio.com) document which, along with the data package, will be available in a public repository^[For peer-review purposes, the data package and code are currently in an anonymous Drive folder: \url{https://drive.google.com/drive/folders/1cT6tcUc1pJ4aT5ajQ0emO0lyS46P8Ige?usp=sharing}].

>>>>

---
output:
  github_document:
    pandoc_args: --webtex
always_allow_html: true
bibliography: [R0-Density-Reanalysis/bibliography.bib, R0-Density-Reanalysis/packages.bib]
---

@@

```{r generate-package-bibliography, include=FALSE}
knitr::write_bib(c(.packages(), 
                   "knitr", 
                   "rmarkdown"), 
                 file = "R0-Density-Reanalysis/packages.bib")
```

@@

The objective of this paper is to illustrate the importance of reproducibility in research in the context of the flood of COVID-19 papers. For this, I focus on a recent study by Sy et al. [-@Sy2021population] that examined the correlation between the basic reproductive number of COVID-19, $R_0$, and population density.  The basic reproductive number is a summary measure of contact rates, probability of transmission of a pathogen, and duration of infectiousness. In rough terms, it measures how many new infections each infections begets. The paper of Sy et al. [-@Sy2021population] was selected for being, in the literature examined, almost alone in supporting reproducible research. Accordingly, I wish to be clear that my objective in singling their work for discussion is not to malign their efforts, but rather to demonstrate how open and reproducible research efforts can greatly help to accelerate discovery. More concretely, open data and open code mean that an independent researcher can, with only modest efforts, not only verify the findings reported, but also examine the same data from a perspective which may not have been available to the original researchers due to differences in disciplinary perspectives, methodological traditions, and/or training, among other possible factors. The example, which shows consequential changes in the conclusions reached by different analyses, should serve as a call to researchers to redouble their efforts to increase transparency and reproducibility in their research. In this spirit, the present paper also aims to show how data can be packaged in well-documented, shareable units, and code can be embedded into self-contained documents suitable for review and independent verification. The source for this paper is an [R Markdown](http://rmarkdown.rstudio.com) document which, along with the data package, are available in a public repository^[\url{https://github.com/paezha/Reproductive-Rate-and-Density-US-Reanalyzed}]
